---
title: "Correlation exploration WF EV"
author: "Sarah Klain"
date: "May 1, 2016"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Setup

```{r}
library(Hmisc) #to run correlations with sig levels
library(corrgram)
library(corrplot) # for great charts
# library(stats) # for PCA
# library(psych)
```

Input data

In cer_2016_01_08_dem4.csv I recoded const_st by removing the 5s, which removes the "not sure" responses
```{r}
setwd("/Users/sarahklain/Documents/R_2015/navi") #set working directory
ev_wf <- read.csv("cer_2016_01_08_dem4.csv")
#str(ev_wf)

```

### Correlations

```{r}
corr1 <- rcorr(as.matrix(ev_wf[11:37]), type = "pearson")
corr1

ev_sn <- read.csv("cer_snip.csv")
 
corr2 <- rcorr(as.matrix(ev_sn), type = "pearson")
corr2

ev_wf2 <-na.omit(ev_wf)
```

Make it visual

#```{r}
library(corrplot)
cp1 <- corrplot(cor(as.matrix(ev_wf2[1:36])), order = "hclust", tl.col='black', tl.cex=.75, na.label.col = "black") 

cp1

cp2 <- corrplot(cor(as.matrix(ev_wf2[1:41])), order = "hclust", tl.col='black', tl.cex=.75, na.label.col = "black") 

cp2
#visual with numbers
cp_num <- corrplot(corr, method = "number", tl.cex = 1, tl.col='black')
cp_num
```{r}
#snippet of dataset
ev_sn2 <- na.omit(ev_sn)
cp_sn <- corrplot(cor(as.matrix(ev_sn2)), order = "hclust", tl.col='black', tl.cex=.75, na.label.col = "black", insig = "pch") 

cp_sn
```

get p values for smaller subset of variables
```{r}
library(psych)
corr.test(ev_wf[11:15], ev_wf[11:15])
corr.test(ev_wf[11:15], ev_wf[38:41])
corr.test(ev_wf[11:15], ev_wf[16:41])
```

oper negatively correlates with other_rel, 
const_st neg corr with clean instr

correlation table with only wind farm attitude questions

```{r}
library(Hmisc)

flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}

res <- rcorr(as.matrix(ev_sn2))
fcm <- flattenCorrMatrix(res$r, res$P)
fcm

#smaller dataset
ev_sn_1 <- read.csv("cer_snip2.csv")
ev_sn_2 <- na.omit(ev_sn_1)
ev_sn_2$att_w_US <- NULL
ev_sn_2$wf_rec <- NULL

res2 <- rcorr(as.matrix(ev_sn_2))
fcm2 <- flattenCorrMatrix(res2$r, res$P)
fcm2
```

Better visual with significance
```{r}
panel.shadeNtext <- function (x, y, corr = NULL, col.regions, ...) 
{
  corr <- cor(x, y, use = "pair")
  results <- cor.test(x, y, alternative = "two.sided")
  est <- results$p.value
  stars <- ifelse(est < 5e-4, "***", 
                  ifelse(est < 5e-3, "**", 
                         ifelse(est < 5e-2, "*", "")))
  ncol <- 14
  pal <- col.regions(ncol)
  col.ind <- as.numeric(cut(corr, breaks = seq(from = -1, to = 1, 
                                               length = ncol + 1), include.lowest = TRUE))
  usr <- par("usr")
  rect(usr[1], usr[3], usr[2], usr[4], col = pal[col.ind], 
       border = NA)
  box(col = "lightgray")
  on.exit(par(usr))
  par(usr = c(0, 1, 0, 1))
  r <- formatC(corr, digits = 2, format = "f")
  cex.cor <- .8/strwidth("-X.xx")
  fonts <- ifelse(stars != "", 2,1)
  # option 1: stars:
  text(0.5, 0.4, paste0(r,"\n", stars), cex = cex.cor)
  # option 2: bolding:
  #text(0.5, 0.5, r, cex = cex.cor, font=fonts)
}

# Generate some sample data
#sample.data <- matrix(rnorm(100), ncol=10)
#sample.data <- matrix(ev_sn_2, ncol = 10)
sample.data <- as.matrix(ev_sn_2, ncol = 8)

# Call the corrgram function with the new panel functions
# NB: call on the data, not the correlation matrix
cg <- corrgram(sample.data, type="data", lower.panel=panel.shadeNtext, 
         upper.panel=NULL)

cg

```



