---
title: "Corr_explore_wf_ev2"
author: "Sarah Klain"
date: "July 13, 2016"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Setup

```{r}
library(Hmisc) #to run correlations with sig levels
library(corrgram)
library(corrplot) # for great charts
# library(stats) # for PCA
# library(psych)
```

Input data

I redid the dataset so wf_corr Likert scales reflect high environmental value with high score. In const_st I removed the "not sure" responses
```{r}
setwd("/Users/sarahklain/Documents/R_2015/navi") #set working directory

#cwf <- read.csv("wf_corr.csv")
cwf <- read.csv("wf_corr2.csv")
cwf2 <-na.omit(cwf)
cwf2 <- cwf[1:11]
```

### Correlations

```{r}
corr1 <- rcorr(as.matrix(cwf[1:12]), type = "pearson")
corr1

cwf2 <- cwf[1:11]
```

Make it visual

#fix later
#```{r}
cp <- corrplot(cor(as.matrix(cwf2[1:5])), order = "hclust", tl.col='black', tl.cex=.75, na.label.col = "black") 

cp

cp2 <- corrplot(cor(as.matrix(ev_wf2[1:41])), order = "hclust", tl.col='black', tl.cex=.75, na.label.col = "black") 

cp2
#visual with numbers
cp_num <- corrplot(corr, method = "number", tl.cex = 1, tl.col='black')
cp_num

get p values for smaller subset of variables
```{r}
library(psych)
corr.test(ev_wf[11:15], ev_wf[11:15])
corr.test(ev_wf[11:15], ev_wf[38:41])
corr.test(ev_wf[11:15], ev_wf[16:41])
```


Better visual with significance
```{r}
panel.shadeNtext <- function (x, y, corr = NULL, col.regions, ...) 
{
  corr <- cor(x, y, use = "pair")
  results <- cor.test(x, y, alternative = "two.sided")
  est <- results$p.value
  stars <- ifelse(est < 5e-4, "***", 
                  ifelse(est < 5e-3, "**", 
                         ifelse(est < 5e-2, "*", "")))
  ncol <- 14
  pal <- col.regions(ncol)
  col.ind <- as.numeric(cut(corr, breaks = seq(from = -1, to = 1, 
                                               length = ncol + 1), include.lowest = TRUE))
  usr <- par("usr")
  rect(usr[1], usr[3], usr[2], usr[4], col = pal[col.ind], 
       border = NA)
  box(col = "lightgray")
  on.exit(par(usr))
  par(usr = c(0, 1, 0, 1))
  r <- formatC(corr, digits = 2, format = "f")
  cex.cor <- .8/strwidth("-X.xx")
  fonts <- ifelse(stars != "", 2,1)
  # option 1: stars:
  text(0.5, 0.4, paste0(r,"\n", stars), cex = cex.cor)
  # option 2: bolding:
  #text(0.5, 0.5, r, cex = cex.cor, font=fonts)
}

# Generate some sample data
#sample.data <- matrix(rnorm(100), ncol=10)
#sample.data <- matrix(ev_sn_2, ncol = 10)
sample.data <- as.matrix(cwf2, ncol = 11)

# Call the corrgram function with the new panel functions
# NB: call on the data, not the correlation matrix
cg <- corrgram(sample.data, type="data", lower.panel=panel.shadeNtext, 
         upper.panel=NULL)

cg

```

Linear model

```{r}
#z <- lm(y ~ x, data = cwf)
lm_at_w_US <- lm(att_w_US ~ NEP + rel + met + moral + instr + gender + age + edu + income + employ, data = cwf)

summary(lm_at_w_US)    # parameter estimates and overall model fit
plot(lm_at_w_US)       # plots of residuals, normal quantiles, leverage
coef(lm_at_w_US)       # model coefficients (means, slopes, intercepts)
confint(lm_at_w_US)    # confidence intervals for parameters

resid(lm_at_w_US)      # residuals
fitted(lm_at_w_US)     # predicted values
abline(lm_at_w_US)     # adds simple linear regression line to scatter plot

lm_const_st <- lm(const_st ~ NEP + rel + met + moral + instr + gender + age + edu + income + employ, data = cwf)

summary(lm_const_st)


lm_first_st <- lm(first_st ~ NEP + rel + met + moral + instr + gender + age + edu + income + employ, data = cwf)

summary(lm_first_st)
```


