---
title: "MT_T_F_value_statements"
author: "Sarah Klain"
date: "May 13, 2016"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Setup

```{r}
library(Hmisc) #to run correlations with sig levels
library(ggplot2) # for great charts
library(ggthemes) # for pretty themes in ggplot
library(viridis) # for pretty colors
library(dplyr)
library(knitr) # tool for making nice tables
library(tidyr) # data table wrangling tool
library(broom)
library(stargazer) # makes pretty tables
# library(stats) # for PCA
# library(psych)
```

### All statements, all populations

Input data
```{r}
setwd("/Users/sarahklain/Documents/R_2015/navi") #set working directory
ev <- read.csv("Env_Val_02_29_2016.csv")
#str(ev)
#head(ev)
```

Bring into dplyr

```{r}
#Env values long form
evl <- tidyr::gather(ev, "val_state", "response", 3:33) #short form to long form data for ease in analysis

#bring into dplyr for ease in extracting one sub-population
evtab <- evl %>%
  tbl_df

# str(evl)
# head(evl)
# View(evtab)
```

Add new column to group data by env value type

```{r}
ev_nep <- evtab %>% 
  filter(val_state == "abuse_nep" | val_state == "bal_r_nep" | val_state == "crisis_r_nep" | val_state == "spaceship_nep" | val_state == "bau_nep") %>% 
  mutate(v_type = "NEP")

ev_inst <- evtab %>% 
  filter(val_state == "extract_r_ins" | val_state == "clean_inst" | val_state == "loss_r_ins") %>% 
  mutate(v_type = "inst")

ev_rel <- evtab %>% 
  filter(val_state == "comm_rel" | val_state == "iden_rel" | val_state == "kin_rel" | val_state == "wild_rel" | val_state == "health_rel2" | val_state == "other_rel" | val_state == "resp_rel" ) %>% 
  mutate(v_type = "rel")

ev_met <- evtab %>% 
  filter(val_state == "kin_met" | val_state == "resp_met" | val_state == "iden_met" | val_state == "other_met") %>% 
  mutate(v_type = "met")

ev_mor <- evtab %>% 
  filter(val_state == "decade_r_mor" | val_state == "right_r_mor") %>% 
  mutate(v_type = "moral")

# View(ev_met)
eval_t2 <- bind_rows(ev_nep, ev_inst, ev_rel, ev_met, ev_mor)
str(eval_t2)
summary(eval_t2)

eval_t3 <- eval_t2 %>% 
  filter(response > 0)
```

Violin plot
```{r}

val_st_vio <- ggplot(eval_t3, aes(x = val_state, y = response, fill = v_type)) +
 geom_violin(adjust=0.3) +
  xlab("Statement") + ylab("Response\n1= stongly disagree; 5 = strongly agree") +
  scale_fill_viridis(discrete=TRUE, "Category of Value\nStatement") +
  ggtitle("To what extent do you agree with these value statements?") +
  coord_cartesian(ylim = c(1, 5)) +
  stat_summary(fun.y=mean, colour="orangered", geom="point", 
               shape=18, size=2)  

val_st_vio
```

Faceted Violin plot by sub-pop
```{r}
val_st_vio_sp <- ggplot(eval_t3, aes(x = val_state, y = response, fill = v_type)) +
 geom_violin(adjust=0.3) +
  xlab("Statement") + ylab("Response\n1= stongly disagree; 5 = strongly agree") +
  scale_fill_viridis(discrete=TRUE, "Category of Value\nStatement") +
  ggtitle("To what extent do you agree with these value statements?") +
  coord_cartesian(ylim = c(1, 5)) +
  stat_summary(fun.y=mean, colour="orangered", geom="point", 
               shape=18, size=2)  +
  facet_grid(~ sub_pop)

val_st_vio_sp
```

Faceted Violin plot by sub-pop for all prompts
```{r}
val_st_vio_sp <- ggplot(eval_t3, aes(x = val_state, y = response, fill = v_type)) +
 geom_violin(adjust=0.3) +
  xlab("Statement") + ylab("Response\n1= stongly disagree; 5 = strongly agree") +
  scale_fill_viridis(discrete=TRUE, "Category of Value\nStatement") +
  ggtitle("To what extent do you agree with these value statements?") +
  coord_cartesian(ylim = c(1, 5)) +
  stat_summary(fun.y=mean, colour="orangered", geom="point", 
               shape=18, size=2)  +
  facet_grid(sub_pop ~.)

val_st_vio_sp
```

Faceted Violin plot by sub-pop, rel and NEP
```{r}
eval_t4 <- eval_t3 %>% 
  filter(v_type != "met") %>% 
  filter(v_type != "moral") %>% 
  filter(v_type != "inst")
#View(eval_t4)

val_st_vio_sp2 <- ggplot(eval_t4, aes(x = val_state, y = response, fill = v_type)) +
 geom_violin(adjust=0.3) +
  xlab("Statement") + ylab("Response\n1= stongly disagree; 5 = strongly agree") +
  scale_fill_viridis(discrete=TRUE, "Category of Value\nStatement") +
  ggtitle("To what extent do you agree with these value statements?") +
  coord_cartesian(ylim = c(1, 5)) +
  stat_summary(fun.y=mean, colour="orangered", geom="point", 
               shape=18, size=2)  +
  facet_grid(sub_pop~.)

val_st_vio_sp2
```

Faceted Violin plot by rel
```{r}

eval_t5 <- eval_t4 %>% 
  filter(v_type == "rel")

val_st_vio_sp3 <- ggplot(eval_t5, aes(x = sub_pop, y = response, fill = sub_pop)) +
 geom_violin(adjust=0.3) +
  xlab("") + ylab("Response\n1= stongly disagree; 5 = strongly agree") +
  scale_fill_viridis(discrete=TRUE, "Sample") +
  ggtitle("Relational Value Statements\nTo what extent do you agree with these statements?") +
  coord_cartesian(ylim = c(1, 5)) +
  stat_summary(fun.y=mean, colour="orangered", geom="point", 
               shape=10, size=3)  +
  facet_grid(~val_state)

val_st_vio_sp3
```

NEP
```{r}
eval_NEP <- eval_t4 %>% 
  filter(v_type == "NEP")

val_st_vio_NEP <- ggplot(eval_NEP, aes(x = sub_pop, y = response, fill = sub_pop)) +
 geom_violin(adjust=0.3) +
  xlab("") + ylab("Response\n1= stongly disagree; 5 = strongly agree") +
  scale_fill_viridis(discrete=TRUE, "") +
  ggtitle("NEP\nTo what extent do you agree with these statements?") +
  coord_cartesian(ylim = c(1, 5)) +
  stat_summary(fun.y=mean, colour="orangered", geom="point", 
               shape=10, size=3)  +
  facet_grid(~val_state)

val_st_vio_NEP
```


### Histogram, all value statements

```{r}
eval_t3$val_state <- factor(eval_t3$val_state, levels=c("extract_r_ins" ,"loss_r_ins","clean_inst", "kin_met", "resp_met", "iden_met","other_met", "decade_r_mor","right_r_mor", "abuse_nep", "bal_r_nep", "crisis_r_nep", "spaceship_nep", "bau_nep", "comm_rel", "wild_rel","resp_rel", "iden_rel", "kin_rel", "health_rel2", "other_rel"))

bar_all <- ggplot(eval_t3, aes(x = response, fill = v_type)) +
  geom_histogram(binwidth = 1) +
  scale_fill_viridis(discrete=TRUE, option = "viridis", "") +
  xlab("Response\n1 = Strongly Disagree;\n2 = Disagree; 3 = Neither Agree nor Disagree;\n4 = Agree; 5 = Strongly Agree") +
  ggtitle("To what extent do you agree with these statements?") +
  coord_cartesian(xlim = c(1, 5)) + coord_flip() +
  facet_grid(~ val_state)
  
bar_all
```

### Histogram by value statement and pop
```{r}
bar_all2 <- ggplot(eval_t3, aes(x = response, fill = v_type)) +
  geom_histogram(binwidth = 1) +
  scale_fill_viridis(discrete=TRUE, option = "viridis", "") +
  xlab("Response\n1 = Strongly Disagree;\n2 = Disagree; 3 = Neither Agree nor Disagree;\n4 = Agree; 5 = Strongly Agree") +
  ggtitle("To what extent do you agree with these statements?") +
  coord_cartesian(xlim = c(1, 5)) + coord_flip() +
  facet_grid(sub_pop ~ val_state)

bar_all2
#ggsave(bar_all, file="/Users/sarahklain/Documents/R_2015/env_val/figs/bar_all.pdf")
```

### Means with error bars
```{r}
val_mean_se <- ggplot(eval_t3, aes(factor(val_state), response, color = v_type, width = 0.25)) +
  stat_boxplot(geom ='errorbar', width = 0.25) +
  geom_boxplot(width = 0.25) +
  scale_color_viridis(discrete=TRUE) +
  ylab("Response\n1 = Strongly Disagree;\n2 = Disagree; 3 = Neither Agree nor Disagree;\n4 = Agree; 5 = Strongly Agree") +
  ggtitle("To what extent do you agree with these statements?") +
  stat_summary(fun.y=mean, geom="point", shape=10, size=2)  +
  #coord_flip() +
  facet_grid(sub_pop~.)

val_mean_se
```


Vio plot with means, NEP and rel

```{r}
val_st_vio_sp_mean <- ggplot(eval_t4, aes(x = v_type, y = response, fill = v_type)) +
 geom_violin(adjust=0.3) +
  xlab("Statement") + ylab("Response\n1 = Strongly Disagree; 2 = Disagree;\n13 = Neither Agree nor Disagree;\n4 = Agree; 5 = Strongly Agree") +
  scale_fill_viridis(discrete=TRUE, "Category \nof Value\nStatement") +
  ggtitle("To what extent do you agree with these value statements?") +
  coord_cartesian(ylim = c(1, 5)) +
  stat_summary(fun.y=mean, colour="orangered", geom="point", 
               shape=10, size=5)  +
  facet_grid(~ sub_pop)

val_st_vio_sp_mean
ggsave(val_st_vio_sp_mean, file="/Users/sarahklain/Documents/R_2015/navi/figs/val_st_vio_sp_mean.jpg")
```

with other value types
```{r}
val_st_vio_mean <- ggplot(eval_t3, aes(x = v_type, y = response, fill = v_type)) +
 geom_violin(adjust=0.3) +
  xlab("Statement") + ylab("Response\n1 = Strongly Disagree 2 = Disagree;\n3 = Neither Agree nor Disagree;\n4 = Agree; 5 = Strongly Agree") +
  scale_fill_viridis(discrete=TRUE, "Category\nof Value\nStatement") +
  ggtitle("To what extent do you agree with these value statements?") +
  coord_cartesian(ylim = c(1, 5)) +
  stat_summary(fun.y=mean, colour="orangered", geom="point", 
               shape=10, size=4)  +
  facet_grid(~ sub_pop)

val_st_vio_mean
#ggsave(val_st_vio_mean, file="/Users/sarahklain/Documents/R_2015/navi/figs/val_st_vio_mean.jpg")
```

```{r}
val_st_bp_mean <- ggplot(eval_t3, aes(x = v_type, y = response, fill = v_type)) +
 geom_boxplot() +
  xlab("Statement") + ylab("Response\n1 = Strongly Disagree 2 = Disagree;\n3 = Neither Agree nor Disagree;\n4 = Agree; 5 = Strongly Agree") +
  scale_fill_viridis(discrete=TRUE, "Category\nof Value\nStatement") +
  ggtitle("To what extent do you agree with these value statements?") +
  coord_cartesian(ylim = c(1, 5)) +
  stat_summary(fun.y=mean, colour="orangered", geom="point", 
               shape=10, size=4)  +
  facet_grid(~ sub_pop)

val_st_bp_mean
#ggsave(val_st_vio_mean, file="/Users/sarahklain/Documents/R_2015/navi/figs/val_st_vio_mean.jpg")
```


```{r}
val_st_bp_mean_all <- ggplot(eval_t3, aes(x = val_state, y = response, fill = v_type)) +
 geom_boxplot() +
  xlab("Statement") + ylab("Response\n1 = Strongly Disagree 2 = Disagree;\n3 = Neither Agree nor Disagree;\n4 = Agree; 5 = Strongly Agree") +
  scale_fill_viridis(discrete=TRUE, "Category\nof Value\nStatement") +
  ggtitle("To what extent do you agree with these value statements?") +
  coord_cartesian(ylim = c(1, 5)) +
  stat_summary(fun.y=mean, colour="orangered", geom="point", 
               shape=10, size=4)  +
  facet_grid(~ sub_pop)

val_st_bp_mean_all
```


```{r}
all_m <- read.csv("all_means.csv")
all_m_t <- all_m %>%
  tbl_df

all_m2 <- all_m_t %>%
  filter(v_type != "met") %>% 
  filter(v_type != "other") %>%
  filter(ave > 0) %>% 
  mutate(value = reorder(value, ave)) %>% 
  arrange(ave)

#cron2 <- cron %>% 
#  mutate(prompt = reorder(prompt, alpha)) %>% 
#  arrange(alpha)

bar_means <- ggplot(all_m2, aes(x = value, y = ave, fill = v_type)) +
  geom_bar(stat = "identity") +
  scale_fill_viridis(discrete=TRUE, option = "viridis", name = "Type of\nValue Prompt") +
  xlab("Social-Ecological Value Prompt") +
  ylab("Response\n1 = Strongly Disagree; 2 = Disagree;\n3 = Neither Agree nor Disagree;\n4 = Agree; 5 = Strongly Agree") + 
  ggtitle("Mean Response to Value Prompts") 

bar_means

```


```{r}
m3p <- read.csv("means_3pop.csv")

#sort by mturk responses

m3p$value <- factor(m3p$value, levels=c("clean", "other","resp", "abuse", "other_m", "comm", "right", "kin", "resp_m", "crisis",  "bau", "spaceship", "decade", "iden", "bal", "loss", "health", "wild", "kin_m", "iden_m", "extract", "tech"))


#sort by tourist responses
#m3p$value <- factor(m3p$value, levels=c("other_m", "iden_m", "resp_m", "kin_m", "clean",	"other",	"resp",	"right",	"comm",	"health",	"iden",	"decade",	"abuse",	"kin",	"bal",	"loss",	"wild",	"crisis",	"bau",	"spaceship",	"tech",	"extract,"))

m3pt <- m3p %>% 
  tbl_df %>% 
#  filter(type1 != "Metaphor") %>% 
  filter(type1 != "Other") # %>% 
  #mutate(value = reorder(value, mean_resp)) %>% 
  #arrange(value)

bar_mean2 <- ggplot(na.omit(m3pt), aes(x = value, y = mean_resp, fill = type1)) +
  geom_bar(stat = "identity", width = 0.75) +
  scale_fill_viridis(discrete=TRUE, option = "viridis", name = "Type of\nValue Prompt") +
  xlab("Social-Ecological Value Prompt") +
  ylab("Response\n1 = Strongly Disagree; 2 = Disagree;\n3 = Neither Agree nor Disagree;4 = Agree; 5 = Strongly Agree") + 
  ggtitle("Mean Response to Value Prompts") +
  facet_grid(sub_pop~.)

bar_mean2
```

calc means for sub pops, relational values

```{r}
eval_rel_f <- eval_t4 %>% 
  filter(v_type == "rel") %>% 
  filter(sub_pop == "Farmer") 

mean(eval_rel_f$response)

eval_rel_mt <- eval_t4 %>% 
  filter(v_type == "rel") %>% 
  filter(sub_pop == "M-Turk") 

mean(eval_rel_mt$response)

eval_rel_to <- eval_t4 %>% 
  filter(v_type == "rel") %>% 
  filter(sub_pop == "Tourist") 

mean(eval_rel_to$response)

```

calc means for sub pops, NEP

```{r}
eval_NEP_f <- eval_t4 %>% 
  filter(v_type == "NEP") %>% 
  filter(sub_pop == "Farmer") 

mean(eval_NEP_f$response)

eval_NEP_mt <- eval_t4 %>% 
  filter(v_type == "NEP") %>% 
  filter(sub_pop == "M-Turk") 

mean(eval_NEP_mt$response)

eval_NEP_to <- eval_t4 %>% 
  filter(v_type == "NEP") %>% 
  filter(sub_pop == "Tourist") 

mean(eval_NEP_to$response)

```

T-tests
Are means for subpops different from each other?

```{r}
library(Hmisc)

#Relational
t.test(eval_rel_f$response, eval_rel_to$response, paired = FALSE)
t.test(eval_rel_mt$response, eval_rel_to$response, paired = FALSE)

#NEP
t.test(eval_NEP_f$response, eval_NEP_to$response, paired = FALSE)
t.test(eval_NEP_f$response, eval_NEP_mt$response, paired = FALSE)
t.test(eval_NEP_mt$response, eval_NEP_to$response, paired = FALSE)
```

```{r}
library(corrplot)
#foo <-na.omit(ev)
#corrplot(cor(as.matrix(foo)), order = "hclust", tl.col='black', #tl.cex=.75, na.label.col = "black") 
```

